Enhancement of SDR in Thessaloniki

### 2024-08-26 GHI_enh_03_process.tex
Commit 2024-08-26 23:11

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-08-25}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
   0.00   89.59  180.00  180.00  270.41  360.00 
\end{verbatim}

\begin{verbatim}
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
-72.8133 -27.4719   0.7629   0.4279  28.2416  83.4876 
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 2 rows containing missing values or values outside the scale range (`geom_line()`).
Removed 2 rows containing missing values or values outside the scale range (`geom_line()`).
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-319.48 -147.87  -56.18  101.04  719.45

Coefficients:
                  Estimate Std. Error t value Pr(>|t|)    
(Intercept)      1.379e+02  4.559e+01   3.025 0.002663 ** 
as.numeric(Date) 1.306e-07  3.650e-08   3.579 0.000391 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 196.3 on 363 degrees of freedom
Multiple R-squared:  0.03409,   Adjusted R-squared:  0.03143 
F-statistic: 12.81 on 1 and 363 DF,  p-value: 0.0003913
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-319.48 -147.87  -56.18  101.04  719.45

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)    
(Intercept)       1.379e+02  4.559e+01   3.025 0.002663 ** 
ST_E_monthly$Date 1.306e-07  3.650e-08   3.579 0.000391 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 196.3 on 363 degrees of freedom
Multiple R-squared:  0.03409,   Adjusted R-squared:  0.03143 
F-statistic: 12.81 on 1 and 363 DF,  p-value: 0.0003913
\end{verbatim}

@@

\begin{verbatim}
2024-08-25 15:41:24.7 athan@tyler GHI_enh_03_process.R 7.859937 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-08-26}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
   0.00   89.59  180.00  180.00  270.42  360.00 
\end{verbatim}

\begin{verbatim}
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
-72.8133 -27.4717   0.7634   0.4285  28.2424  83.4876 
\end{verbatim}

@@

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-316.47 -148.10  -55.61  103.32  718.33

Coefficients:
                  Estimate Std. Error t value Pr(>|t|)   
(Intercept)      1.520e+02  4.805e+01   3.164  0.00169 **
as.numeric(Date) 1.205e-07  3.816e-08   3.157  0.00173 **
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 197.8 on 354 degrees of freedom
Multiple R-squared:  0.02738,   Adjusted R-squared:  0.02463 
F-statistic: 9.966 on 1 and 354 DF,  p-value: 0.001732
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-316.47 -148.10  -55.61  103.32  718.33

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)   
(Intercept)       1.520e+02  4.805e+01   3.164  0.00169 **
ST_E_monthly$Date 1.205e-07  3.816e-08   3.157  0.00173 **
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 197.8 on 354 degrees of freedom
Multiple R-squared:  0.02738,   Adjusted R-squared:  0.02463 
F-statistic: 9.966 on 1 and 354 DF,  p-value: 0.001732
\end{verbatim}

@@

\begin{verbatim}
2024-08-26 19:50:18.2 athan@sagan GHI_enh_03_process.R 3.387402 mins
\end{verbatim}

### 2024-08-26 GHI_enh_04_investigate.tex
Commit 2024-08-25 00:10
Commit 2024-08-26 23:11

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-08-24}

@@

\caption{ - empty caption - }\label{fig:groups-5}
\end{figure}
\begin{figure}[H]

@@

\begin{verbatim}
Warning: Removed 252 rows containing non-finite outside the scale range
(`stat_bin()`).
\end{verbatim}

\begin{verbatim}
Warning: Removed 28187 rows containing non-finite outside the scale range
(`stat_bin()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 252 rows containing non-finite outside the scale range (`stat_bin()`).
Removed 28187 rows containing non-finite outside the scale range (`stat_bin()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 252 rows containing non-finite outside the scale range (`stat_bin()`).
Removed 28187 rows containing non-finite outside the scale range (`stat_bin()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 16 rows containing non-finite outside the scale range
(`stat_bin2d()`).
\end{verbatim}

@@

\begin{verbatim}
2024-08-24 16:34:51.8 athan@tyler GHI_enh_04_investigate.R 2.043213 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-08-26}

@@

\caption{ - empty caption - }\label{fig:groups-5}
\end{figure}

\begin{verbatim}
Warning: Removed 246 rows containing non-finite outside the scale range
(`stat_bin()`).
\end{verbatim}

\begin{verbatim}
Warning: Removed 27787 rows containing non-finite outside the scale range
(`stat_bin()`).
\end{verbatim}

@@

@@

\begin{verbatim}
Warning: Removed 246 rows containing non-finite outside the scale range
(`stat_bin()`).
Removed 27787 rows containing non-finite outside the scale range
(`stat_bin()`).
\end{verbatim}

\begin{verbatim}
Warning: Removed 246 rows containing non-finite outside the scale range
(`stat_bin()`).
Removed 27787 rows containing non-finite outside the scale range
(`stat_bin()`).
\end{verbatim}

@@

@@

\begin{verbatim}
Warning: Removed 15 rows containing non-finite outside the scale range
(`stat_bin2d()`).
\end{verbatim}

@@

\begin{verbatim}
2024-08-26 19:52:09.6 athan@sagan GHI_enh_04_investigate.R 0.838254 mins
\end{verbatim}
